---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

ggbiplot2
========

An implementation of the biplot using ggplot2.  The package provides two functions: `ggscreeplot()` and `ggbiplot2()`.
`ggbiplot2` aims to be a drop-in replacement for the built-in R function `biplot.princomp()` with extended functionality 
for labeling groups, drawing a correlation circle, and adding Normal probability ellipsoids.

*The development of this software was supported in part by NSF Postdoctoral Fellowship DMS-0903120*

Installation
------------

```r
library(devtools)
install_github("deprekate/ggbiplot2")
```

Example Usage
-------------

```{r wine-example, message = FALSE, warning = FALSE}
library(ggbiplot2)
data(wine)
wine.pca <- prcomp(wine, scale. = TRUE)
ggbiplot2(wine.pca, obs.scale = 1, var.scale = 1,
  groups = wine.class, ellipse = TRUE, circle = TRUE) +
  scale_color_discrete(name = '') +
  theme(legend.direction = 'horizontal', legend.position = 'top')
```
